Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-01 paper/ms.tex
Remove otherstudies table; doubting its costeffectiveness
add boring title
enhance figure captions and restructure data (WIP)

\title{Kronos \& Krios: TBD}

@@

Though previously recognized as a visual double star system
(\citealt{2001AJ....122.3466M}), \sunanalog\ and \bizarreone\ were identified as a
candidate comoving star pair in our recent search for comoving stars using the
proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (proper motions).
We then select a sample of high-confidence comoving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2016arXiv161202440O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
analyzed high resolution spectra of both stars obtained using HIRES spectrograph
on Keck~I telescope.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164-7799$~\AA.
Typical signal-to-noise ratio in continuum is $>200$~per pixel.
The resulting measurements include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:kk}.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.

Combining these precise radial velocities with the \gaia\ astrometry, we can
compare differences between the inferred 6D phase-space properties for the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
given the observed parallax, $\pi$, and proper motion components,
$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
By defining the vectors
% SMOH: I understand you meant hat v_r as the latent true radial velocity but
% personally think a) it can confuse some people that there are hat quantities
% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
% quantities for observed variables and no-hat for latent true ones.
% SMOH: v_r is missing in the LHS of eq(3)
\begin{eqnarray}
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \pi &
          \mu_{\alpha^*} &
          \mu_\delta &
          v_r
        \end{array}
      \right)}\\
  \hat{\vec{y}} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          \hat{v}_r
        \end{array}
      \right)}
\end{eqnarray}
and by considering the covariance matrix $\mat{C}$ between the observed
quantities (provided by \tgas\ and extended to include the uncorrelated radial
velocity uncertainty), the likelihood can be written
\begin{eqnarray}
p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
    \mat{C}^{-1} \,
    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
\end{eqnarray}
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
For each of the two stars, we use \project{emcee}
(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
first 512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
etc.}).
\figname~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
In all components, the pair is consistent with being comoving and close in
separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
but the median 3-space separation is $\approx$$0.6~\pc$.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone.
    \label{fig:dxdv}}
\end{figure}

\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
explain}
The Sun's orbit in this same Milky Way model is under-plotted for comparison
(grey line); the orbits of the stars in this pair have large scale-heights
relative to the Sun's orbit despite being young.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{%
    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
    For \sunanalog\, the initial conditions are set to the median posterior
    sample over the inferred 6D phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
    Leapfrog integration scheme implemented in \project{Gala}
    (\citealt{Gala:2017}). \todo{APW: citation...}
\label{fig:orbit}}
\end{figure}

Given their proximity in space and kinematics,
it is generally accepted to assume that the two stars were born coeval
perhaps in a wide binary from the same birth cloud.
Thus, we expect the two stars to have identical metallicities and abundance patterns,
\todo{except for thoese elements like Li...}
Surprisingly, one of the stars, \bizarreone\ is significantly more metal
rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
What is more puzzling is that the abundances of this star
shows selective depletion in C, N, O, Na, and Mn.

The abundance of \bizarreone\ is peculiar on its own compared to other disk stars with
similar $[\elem{Fe}/\elem{H}]$.
For a star with $[\elem{Fe}/\elem{H}] \approx 0.2$, we generally expect
$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\ ever more unlikely.
We stress that none of the other seven binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
In fact, no strong trend is found in pair for most elements
except N and Y.
For Y, the trend for this pair is opposite of the others in Teff.
Specifically, no difference within pair is found for Mn.
(see figure X in that paper; purple is this pair)

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{isochrones.png}
  \caption{Isochrone ages of \sunanalog\ and \bizarreone.
    On the left, we show the two stars on $T_\mathrm{eff}-\log(g)$ plane,
    and on the right, the color-magnitude diagram using \gaia\ $G$ band
    and \tmass\ $J$ band magnitudes.
    In each panel, \project{MIST} isochrones (\citealt{Choi:2016aa}) at $28$~Myr and $2$~Gyr are
    plotted. The thicker and thinner lines are for $\feh = 0.$ and $0.2$,
    corresponding to values of \sunanalog\ and \bizarreone.
  }
  \label{fig:isochrones}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{sed.png}
  \caption{Spectral energy distributions (SEDs) of \sunanalog\ and \bizarreone.
    The yellow line is the SED of a blackbody at $T=5878$ scaled arbitrarily.
  }
  \label{fig:sed}
\end{figure}

The fact that the two stars share a very similar space motion
at a separation of $0.6$~pc strongly argues that the pair is coeval.
We consider other age indicators apart from their phase space coordinates
to assess the ages and coevality of the two stars.
First, given the precise measurements of $\log(g)$, $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We perform isochrone fitting using the Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.
The isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone.}
  \label{fig:abundances}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
    as a function of condensation temperature of elements (\citealt{2003ApJ...591.1220L}).
  }
  \label{fig:relabun_tcrank}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{deltaXH_Tc_violins.png}
  \caption{Difference in abundances of this pair and other binary pairs in
    \citealt{2016ApJS..225...32B}.
    Additionally, we show the distribution of abundance difference
    between stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments
    by randomly pairing up single stars at two metallicity bins similar to
    the pair of interest.
    The difference is always relative to the lower-$[\elem{Fe}/\elem{H}]$ star.
  }
  \label{fig:deltaXH}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{toycalc.pdf}
  \caption{Solar surface abundance change expected from adding $20~\mearth$ of
    material with bulk Earth or CI chondrite composition.
    The assumed mass fraction in the convective zone is $0.03$.
    For bulk earth composition, which is a closer match to the abundance difference
    seen in \bizarreone\ and \sunanalog, we indicate measured elements with black boundary
    lines around symbols.
  }
  \label{fig:toycalc}
\end{figure}

\input{otherstudies.tex}

We summarize the few wide separation common proper motion pairs that have been
studied in detailed chemical abundance so far.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
Main properties of the systems relevant to the present discussion are
summarized in \tablename~\ref{tab:otherstudies}.
Their reported abundance differences $\Delta\elemH{X}$ where the difference is
always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
comparison with this pair.

@@

% Useful follow up efforts
We discuss the follow up efforts that would be useful to further
illuminate the peculiar abundance difference between the pair.

@@

% Concluding remarks

>>>>

\title{Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone\
    normalized to \elem{H} (top) and \elem{Fe} (bottom).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to \sunanalog\
    along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca}, \elem{Ti}, \elem{V},
    \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
  }
  \label{fig:abundances}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
  \caption{Difference in abundances of this pair and other wide binaries in
    \citealt{2016ApJS..225...32B}.
    Additionally, we show the distribution of abundance difference
    between stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments
    by randomly pairing up single stars in \citealt{2016ApJS..225...32B} at two metallicity bins,
    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
    similar to \bizarreone\ and \sunanalog.
    The difference is always taken to be $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
    Thus, the narrower range of in $\Delta\feh$ is by construction.
    First, we see that most of the other comoving wide binaries included in \citealt{2016ApJS..225...32B}
    have small ($<0.1$~dex) differences in all elements making a difference of $\approx 0.2$~dex seen in
    \bizarreone-\sunanalog\ pair rare.
    Second, random pairings of disk stars with similar $\Delta\feh$ usually show
    similar enhancement in all other elements.
    %Notably, the relative depletion of \elem{Na} and \elem{Mn} with respect to \elem{Fe}
    %suggests that even when we assume \bizarreone\ and \sunanalog\ are of different origin,
    %Galactic evolution cannot explain the difference.
  }
  \label{fig:deltaXH}
\end{figure}

\sunanalog\ and \bizarreone\ were identified as a
candidate comoving star pair in our recent search for comoving stars using the
proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (proper motions).
We then select a sample of high-confidence comoving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2016arXiv161202440O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, \citet{2016ApJS..225...32B} analyzed high resolution
spectra of both stars obtained using HIRES spectrograph on Keck~I telescope.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164-7799$~\AA.
Typical signal-to-noise ratio in continuum is $>200$~per pixel.
The resulting measurements include abundances measured for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
and high precision radial velocities.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.
The \elem{Li} doublet at $6707.6$~\AA\ for this sample was
investigated in a separate work (\citealt{jmlithium}).
We list all spectroscopic measurements including
the absolute abundance\footnote{
  Absolute abundance of element \elem{X} is $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
  where $n_\elem{X}$ is the number density of element \elem{X}.
} of \elem{Li} for the two stars in Table~\ref{tab:kk}.

%In all components, the pair is consistent with being comoving and close in
%separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
%but the median 3-space separation is $\approx$$0.6~\pc$.

%\begin{figure}[htbp]
%  \begin{center}
%    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
%  \end{center}
%  \caption{%
%    Differences in posterior samples over Galactocentric phase-space coordinates
%    for the two stars \sunanalog\ and \bizarreone.
%    \label{fig:dxdv}}
%\end{figure}

%\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
%sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
%in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
%explain}
%The Sun's orbit in this same Milky Way model is under-plotted for comparison
%(grey line); the orbits of the stars in this pair have large scale-heights
%relative to the Sun's orbit despite being young.

%\begin{figure}[htbp]
%  \begin{center}
%    \includegraphics[width=\linewidth]{orbits.pdf}
%  \end{center}
%  \caption{%
%    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
%    For \sunanalog\, the initial conditions are set to the median posterior
%    sample over the inferred 6D phase-space coordinates.
%    The orbits are computed by integrating backwards from the present-day
%    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
%    Leapfrog integration scheme implemented in \project{Gala}
%    (\citealt{Gala:2017}). \todo{APW: citation...}
%\label{fig:orbit}}
%\end{figure}

Although selected based only on their proper motions, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
confirming that they are comoving in all directions.
The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Given their proximity in phase space, it is generally accepted to assume that
the two stars were born together perhaps to form a wide binary system from the
same birth cloud.
Thus, we expect the two stars to have identical metallicities and abundance patterns.
Surprisingly, however, one of the stars, \bizarreone\ is significantly more metal
rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
What is more puzzling is that not all elements are equally enhanced:
the abundances of \bizarreone\ shows selective depletion in
\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
relative to \elem{Fe}.

The validity of the measured abundance differences is further demonstrated
in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
segments of the spectra and model of the two stars.
As expected from metallicity difference ($\Delta\feh \approx 0.2$),
the ratio of data and model between the two stars show significant
residuals of almost all metal features, largely dominated by \elem{Fe}.
However, for lines of elements that are not as enhanced in \bizarreone\,
the residuals are much smaller in amplitude.
%Li?

We stress that none of the other four twin-like ($\Delta T_mathrm{eff} \lesssim 100$~K)
wide binary pairs examined in \citealt{2016ApJS..225...32B} show discrepancies in abundances between the
stars at this level (\figname~\ref{fig:deltaXH}).
As shown in \figname~\ref{fig:deltaXH}, 
In fact, no strong trend is found in pair for most elements
except N and Y.
For Y, the trend for this pair is opposite of the others in Teff.
Specifically, no difference within pair is found for Mn.
(see figure X in that paper; purple is this pair)
Moreoever, the abundance differences cannot be due to different chemical enrichment
history in the disk even if the two stars were of different origin.
\figname~\ref{fig:deltaXH} shows the distribution of $\Delta[\elem{X}/\elem{H}]$
for random pairings of two stars from similar \feh\ as \bizarreone\ and \sunanalog
as violins for each element.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are enhanced at a similar level with some variations.
% Clean up:
% Specifically, it is very unlikely that the star 
% The abundance of \bizarreone\ is peculiar on its own compared to other disk
stars with similar \feh.
%For a star with $\feh \approx 0.2$ like \bizarreone, we generally expect
%$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
%(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\
%very unlikely to arise from Galactic chemical evolution.

The fact that the two stars share a very similar space motion
at a separation of $\approx 0.6$~pc strongly argues that the pair is coeval.
We consider other age indicators apart from their phase space coordinates
to assess the ages and coevality of the two stars.
First, given the precise measurements of $\log(g)$, $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We perform isochrone fitting using the Yale-Yonsei model isochrones (\citealt{2013ApJ...776...87S}).
The input data are $\log(g)$, $T_\mathrm{eff}$, \feh, parallaxes, $B$-band magnitudes, and their errors.
The isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance of \bizarreone\ ($[\mathrm{Fe}/\mathrm{H}] = 0.20$)
    relative to \sunanalog\ ($[\mathrm{Fe}/\mathrm{H}] = 0.01$)
    ranked by the condensation temperature of elements in solar composition gas
    from \citealt{2003ApJ...591.1220L}.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citealt{Mack:2014aa}), XO-2N/S (\citealt{Biazzo:2015aa}),
    and WASP-94AB (\citealt{Teske:2016aa}).
    Note that multiple values are reported 
  }
  \label{fig:relabun_tcrank}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{toycalc.pdf}
  \caption{Expected change in solar surface abundance after adding $20~\mearth$ of
    material with bulk Earth composition (\citealt{mcdonough2001composition}).
    The assumed mass fraction in the convective zone is $0.03$.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $20~\mearth$ of rocky planetary material.
    We elements measured for \bizarreone-\sunanalog\ pair are filled with purple
    while those without measurements are left empty.
  }
  \label{fig:toycalc}
\end{figure}

We summarize the few wide separation common proper motion pairs that have been
studied in detailed chemical abundance so far.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
Their reported abundance differences $\Delta\elemH{X}$ where the difference is
always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
comparison with this pair.

@@

@@

% Concluding remarks
% include Useful follow up efforts
